A Reduced Representation for Computational Fabrication

### 2013-05-03 thesis/Conclusion.tex
we I tense

\chapter{Conclusion}
In this proposal I have taken the first step towards solving an open problem in computational fabrication --  creating a general translation process that transforms user-defined model specifications into printer and material-specific representations. Our process relies on two data structures to make this general translation process expressive and computationally tractable: a \emph{reducer tree} and a \emph{tuner network}. We have shown how existing instances of this translation can be expressed and combined within our system. We believe that our API and its reference implementation will simplify and encourage development of new translation processes.

Our framework offers many exciting opportunities for future work. First, it would be extremely useful to implement many additional simulators in order to allow computing a variety of other properties, e.g., structural soundness, stability, material cost, and printing time. These simulators could be employed to expand the range of possible user-defined specifications. Similarly, only relatively simple error metrics have been tested within the tuning process. The development of more sophisticated and, in particular, perceptually-driven material metrics remains a relatively unexplored research area. Finally, it would be very beneficial to couple our API with a visual interface to further simplify the task of translator construction. It is not obvious what the best visual interface for specifying functional or physical properties of these objects is and more research in this area is necessary.

>>>>

\chapter{Conclusion}
In this proposal I have taken the first step towards solving an open problem in computational fabrication --  creating a general translation process that transforms user-defined model specifications into printer and material-specific representations.
My process relies on two data structures to make this general translation process expressive and computationally tractable: a \emph{reducer tree} and a \emph{tuner network}.
I will show how existing instances of this translation can be expressed and combined within my system.
I believe that my API and its reference implementation will simplify and encourage development of new translation processes.

My system can offer many exciting opportunities for future work.
First, it would be extremely useful to implement many additional simulators in order to allow computing a variety of other properties, e.g., structural soundness, stability, material cost, and printing time.
These simulators could be employed to expand the range of possible user-defined specifications.
Similarly, only relatively simple error metrics have been proposed within the tuning process.
The development of more sophisticated and, in particular, perceptually-driven material metrics remains a relatively unexplored research area.
Finally, it would be very beneficial to couple my API with a visual interface to further simplify the task of translator construction.
It is not obvious what the best visual interface for specifying functional or physical properties of these objects is and more research in this area is necessary.

### 2013-05-03 thesis/DataStructures.tex
we I tense

\chapter{Data Structures}
\label{chap:struct}
\biglet{I}{n} this section, I describe the structure of the \emph{reducer tree} as well as all types of \emph{reducer nodes} implemented in our framework. We also show the structure of individual \emph{tuners} and how they can be arranged into the \emph{tuner network}.

\section{The Reducer Tree}
 Estimating material assignments at output device resolution is computationally intractable. Therefore, material assignment has to be computed using a reduced representation. We specify this representation using a \emph{reducer tree}. This structure is conceptually similar to those used in programmable shading systems (such as Cook's shade trees~\shortcite{Cook1984} or Maya Shader Networks). These systems are primarily concerned with assigning known materials and textures to an object's surface whereas we are seeking an optimal volumetric assignment from a defined set of materials. In order to accomplish this task, we build a tree-based data structure which contains the entire object volume as its root node. We define two classes of \emph{reducer nodes}: \emph{geometry nodes} and \emph{material nodes}.

\paragraph{Geometry Nodes:}A \emph{geometry node} takes a volumetric region as input and produces a partition of this region into smaller sub-regions. 
These can be attached to the object geometry or they can be defined in a global coordinate system.
To demonstrate the flexibility of the \emph{reducer tree}, we define a small yet powerful set of partitioning nodes which are described as follows %used in our prototype
 (\autoref{fig:geometryNodes}):\vspace{-0.25\baselineskip}
\begin{itemize}
\item Plane Node --  partitions the space into two half-spaces, \vspace{-0.25\baselineskip}
\item Column Node -- takes as input the number of columns and accordingly partitions the space,\vspace{-0.25\baselineskip}
\item Voxel Node -- takes as input voxel size and uniformly partitions the space,\vspace{-0.25\baselineskip}
\item B-spline Node -- partitions a volume into two regions cut by a B-spline,\vspace{-0.25\baselineskip}
\item Stratum Node -- takes a single positive distance parameter as an input and partitions the volume into two regions divided by the iso-distance surface.\vspace{-0.25\baselineskip}
\end{itemize}

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figure/geometryNodes}
\caption{2D representations  of the \emph{geometry nodes} used in our \emph{reducer tree}.}
\label{fig:geometryNodes}
\end{figure}

\paragraph{Material Nodes:} The \emph{leaf nodes} of the \emph{reducer tree} are the material parameterization nodes. These contain a material assignment function $\lambda\left(x\right)$ that maps spatial coordinates to materials. We allow our \emph{material nodes} to assign a void material to regions of the volume. Hence, surface displacements and material assignments can be treated in a unified fashion.
While \emph{material node} can be extended to implement arbitrary material assignment functions (such as Functionally Graded Materials), all the following results require only a single type of \emph{material node}, \emph{layered node}, which assigns $k$ material layers of varying thickness to a geometry partition. We can even assign a constant material to a region using a \emph{layered node} with a single layer.

\emph{Geometry nodes} and \emph{material nodes} can be connected into a tree structure that describes a material assignment function throughout the input geometry. 
The essential property of this data structure is that it naturally adapts to the input geometry. This key feature allows it to be reused for different shapes.
\autoref{fig:red1} shows two examples of \emph{reducer trees} and the resulting geometric distributions of materials.
Since the tree describes a nested set of partitions, we can efficiently perform material queries by passing a query point through the tree until it arrives at a parameterization node. 
We note that the \emph{reducer tree} does not inherently enforce material continuity between disjoint regions of the object; however, for material assignment problems, this is neither required nor desired.

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figure/redNetworkNew.pdf}
\caption{Two examples of our \emph{reducer tree}. Left: in order to create an object producing a caustic, the input shape is first divided into columns. Next, each column is sliced by a plane.
By assigning materials to lower parts of the columns, the microfacet surface is created.
Right: a textured object with subsurface scattering properties is produced by first dividing the input shape using a \emph{stratum node}. Then, the outer layer is sliced into columns, which create a texture once materials are assigned. The inner part of the object obtains a material with given subsurface scattering properties.  
}
\label{fig:red1}
\end{figure}

\section{Tuners and Tuning the Reducer Tree}
We define \emph{tuners} as an abstract interface between a \emph{reducer node} and an optimization algorithm. 
A \emph{reducer node} has parameters that control its space partitioning and material composition, e.g., \emph{stratum node} has a parameter which determines its thickness, \emph{column node} has parameters that control the width of columns.
A \emph{tuner} is responsible for tuning these parameters to achieve a specified goal.
A \emph{tuner} is comprised of an optimization scheme, an error metric, a simulator and a goal (\autoref{fig:tuner0}). 
In order to create an optimal material assignment, \emph{tuner nodes} must be attached to the \emph{reducer tree}. The developer links each \emph{tuner} to a \emph{reducer node} in the \emph{reducer tree}. Each \emph{tuner} then traverses the \emph{reducer subtree} (rooted at this \emph{reducer node}) and constructs a parameter list by querying each visited \emph{reducer node}. The developer can label parameters as fixed or free. \emph{Tuner nodes} contain specific optimization routines (e.g., a quadratic program solver). The \emph{tuner node} then uses this routine to optimize its associated free parameters. During execution, additional information (e.g., parameters, errors, etc.) from neighboring Tuner Nodes can be obtained via the \emph{tuner network} (Section~\ref{sec:TunerNetwork}).  Tuner execution can be scheduled (again by the programmer) allowing both serial and parallel processing.

@@

\section{Tuner Network}
\label{sec:TunerNetwork}
For many fabrication problems, \emph{tuners} should not act in isolation. For instance, an optimal material assignment at a given point depends on the material assignment in the neighborhood. Tuning the free parameters without taking into account this dependency usually yields suboptimal results. Therefore, we allow the \emph{tuners} to share information according to a user-specified graph structure. This allows our framework to interface with a wide range of existing graph-based optimization and inference algorithms. For example, Figure~\ref{fig:combine} (right) shows one of the \emph{tuner networks} used in our experiments.
In this network, each node is connected to its four neighbors. In Figure~\ref{fig:ReducerTreesAdditional}, \emph{tuners} enclosed in dashed boxes are connected in this form. \emph{Tuner networks} do not always exhibit this regular connectivity. For instance, \emph{tuners} can be completely unconnected (\autoref{fig:combine} (left) or be organized into groups which feature intra- but not inter-group connections.

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figure/tunedrt.pdf}
\caption{ 
	Left: Two \emph{tuners} attached to a \emph{reducer tree}. Each \emph{tuner} is responsible for tuning the nodes in its attached subtree (denoted by shapes with similarly colored outlines). 
	Right: One type of \emph{tuner network} used in our experiments.}
\label{fig:combine}
\end{figure}

>>>>

\chapter{Data Structures}
\label{chap:struct}
\biglet{I}{n} this section, I describe the structure of the \emph{reducer tree} as well as all types of \emph{reducer nodes} that will be implemented in my framework. I also show the structure of individual \emph{tuners} and how they can be arranged into the \emph{tuner network}.

\section{The Reducer Tree}
Estimating material assignments at output device resolution is computationally intractable. Therefore, material assignment has to be computed using a reduced representation. A developer specifies this representation using a \emph{reducer tree}. This structure is conceptually similar to those used in programmable shading systems (such as Cook's shade trees~\shortcite{Cook1984} or Maya Shader Networks). 
These systems are primarily concerned with assigning known materials and textures to an object's surface whereas I am seeking an optimal volumetric assignment from a defined set of materials. 
In order to accomplish this task, a developer builds a tree-based data structure which contains the entire object volume as its root node. 
I define two classes of \emph{reducer nodes}: \emph{geometry nodes} and \emph{material nodes}.

\paragraph{Geometry Nodes:}A \emph{geometry node} takes a volumetric region as input and produces a partition of this region into smaller sub-regions. 
These can be attached to the object geometry or they can be defined in a global coordinate system.
To demonstrate the flexibility of the \emph{reducer tree}, I define a small yet powerful set of partitioning nodes which are described as follows 
 (\autoref{fig:geometryNodes}):\vspace{-0.25\baselineskip}
\begin{itemize}
\item Plane Node --  partitions the space into two half-spaces, \vspace{-0.25\baselineskip}
\item Column Node -- takes as input the number of columns and accordingly partitions the space,\vspace{-0.25\baselineskip}
\item Voxel Node -- takes as input voxel size and uniformly partitions the space,\vspace{-0.25\baselineskip}
\item B-spline Node -- partitions a volume into two regions cut by a B-spline,\vspace{-0.25\baselineskip}
\item Stratum Node -- takes a single positive distance parameter as an input and partitions the volume into two regions divided by the iso-distance surface.\vspace{-0.25\baselineskip}
\end{itemize}

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figure/geometryNodes}
\caption{2D representations  of the \emph{geometry nodes} used in \emph{reducer trees}.}
\label{fig:geometryNodes}
\end{figure}

\paragraph{Material Nodes:} The \emph{leaf nodes} of the \emph{reducer tree} are the material parameterization nodes. These contain a material assignment function $\lambda\left(x\right)$ that maps spatial coordinates to materials. \emph{Material nodes} can assign a void material to regions of the volume. Hence, surface displacements and material assignments can be treated in a unified fashion.
While \emph{material node} can be extended to implement arbitrary material assignment functions (such as Functionally Graded Materials), all the following results require only a single type of \emph{material node}, \emph{layered node}, which assigns $k$ material layers of varying thickness to a geometry partition.
As a special case, a constant material for a region can be implemented as a \emph{layered node} with a single layer.

\emph{Geometry nodes} and \emph{material nodes} can be connected into a tree structure that describes a material assignment function throughout the input geometry. 
The essential property of this data structure is that it naturally adapts to the input geometry. This key feature allows it to be reused for different shapes.
\autoref{fig:red1} shows two examples of \emph{reducer trees} and the resulting geometric distributions of materials.
Since the tree describes a nested set of partitions, it can efficiently perform material queries by passing a query point through the tree until it arrives at a parameterization node. 
Note that the \emph{reducer tree} does not inherently enforce material continuity between disjoint regions of the object; however, for material assignment problems, this is neither required nor desired.

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figure/redNetworkNew.pdf}
\caption{Two examples of \emph{reducer trees}. Left: in order to create an object producing a caustic, the input shape is first divided into columns. Next, each column is sliced by a plane.
By assigning materials to lower parts of the columns, the microfacet surface is created.
Right: a textured object with subsurface scattering properties is produced by first dividing the input shape using a \emph{stratum node}. Then, the outer layer is sliced into columns, which create a texture once materials are assigned. The inner part of the object obtains a material with given subsurface scattering properties.  
}
\label{fig:red1}
\end{figure}

\section{Tuners and Tuning the Reducer Tree}
I define \emph{tuners} as an abstract interface between a \emph{reducer node} and an optimization algorithm. 
A \emph{reducer node} has parameters that control its space partitioning and material composition, e.g., \emph{stratum node} has a parameter which determines its thickness, \emph{column node} has parameters that control the width of columns.
A \emph{tuner} is responsible for tuning these parameters to achieve a specified goal.
A \emph{tuner} is comprised of an optimization scheme, an error metric, a simulator and a goal (\autoref{fig:tuner0}). 
In order to create an optimal material assignment, \emph{tuner nodes} must be attached to the \emph{reducer tree}. The developer links each \emph{tuner} to a \emph{reducer node} in the \emph{reducer tree}. Each \emph{tuner} then traverses the \emph{reducer subtree} (rooted at this \emph{reducer node}) and constructs a parameter list by querying each visited \emph{reducer node}. The developer can label parameters as fixed or free. \emph{Tuner nodes} contain specific optimization routines (e.g., a quadratic program solver). The \emph{tuner node} then uses this routine to optimize its associated free parameters. During execution, additional information (e.g., parameters, errors, etc.) from neighboring Tuner Nodes can be obtained via the \emph{tuner network} (Section~\ref{sec:TunerNetwork}).  Tuner execution can be scheduled (again by the programmer) allowing both serial and parallel processing.

@@

\section{Tuner Network}
\label{sec:TunerNetwork}
For many fabrication problems, \emph{tuners} should not act in isolation. For instance, an optimal material assignment at a given point depends on the material assignment in the neighborhood. Tuning the free parameters without taking into account this dependency usually yields suboptimal results. Therefore, I allow the \emph{tuners} to share information according to a user-specified graph structure. This allows my framework to interface with a wide range of existing graph-based optimization and inference algorithms. For example, Figure~\ref{fig:combine} (right) shows one of the \emph{tuner networks}.
In this network, each node is connected to its four neighbors. In Figure~\ref{fig:ReducerTreesAdditional}, \emph{tuners} enclosed in dashed boxes are connected in this form. \emph{Tuner networks} do not always exhibit this regular connectivity. For instance, \emph{tuners} can be completely unconnected (\autoref{fig:combine} (left) or be organized into groups which feature intra- but not inter-group connections.

\begin{figure}[h]
\centering
\includegraphics[width=0.7\linewidth]{figure/tunedrt.pdf}
\caption{ 
	Left: Two \emph{tuners} attached to a \emph{reducer tree}. Each \emph{tuner} is responsible for tuning the nodes in its attached subtree (denoted by shapes with similarly colored outlines). 
	Right: One example of \emph{tuner network} that will be used in experiments.}
\label{fig:combine}
\end{figure}

### 2013-05-03 thesis/Results.tex
we I tense

\chapter{Proposed Experiments}
\label{chap:results}
\begin{figure*}[t]
\includegraphics[width=\linewidth]{figure/TexturedExamples.pdf}
\caption {The reducer-tuner model should enable creating objects of arbitrary shapes with embedded textures.}
\label{fig:texturedExamples}
\end{figure*}
\biglet{I}{n} order to evaluate capabilities of our system, I will implement a number of existing translation processes.
Furthermore, the ease with which different algorithm components can be combined enabled creation of two new translation processes.
The first is an algorithm that can produce objects with desired refractive properties and an associated texture.

The second allows us to apply a desired texture to an object with prescribed deformation behavior.
All of these processes, both from prior work and new ones, easily fit into our framework, and were manufactured using a Stratasys Object500 Connex  multi-material printer.
The following paragraphs provide a detailed description of how the individual algorithms were designed with our system.
All \emph{reducer trees} and the \emph{tuner networks} used for producing these results are presented in \autoref{fig:ReducerTreesAdditional}.

\paragraph{Spatially-varying Albedo:}
We have designed a Spec2Fab translator that allows for 3D printing of textured models (Figure~\ref{fig:texturedExamples}).
Being able to apply precisely specified spatially-varying albedo values to printed models is a crucial capability.
However, no standard processes have been designed for this task so far. The input to our algorithm is a shape and its desired albedo texture. Since the texture is only affected by materials close to the surface, we use a \emph{stratum node} to divide the input shape into a thin shell and an inner volume. We then divide the outer layer into columns. The set of printable colors is expanded by stacking translucent materials using the \verb|LayeredMaterial| Node.
The number of layers is fixed to the number of print materials. The reduced parameters are the thickness values of each material layer. For each column, the \emph{tuner}'s optimizer looks up the proper stacking that produces the closest albedo value. Due to printer resolution, the range of albedo values that can be achieved is quantized. We therefore implement an error diffusion algorithm by connecting neighboring \emph{tuners}. In this simple algorithm, the simulation is a table lookup -- we measure the albedo value corresponding to different base materials.

\paragraph{Heterogeneous Subsurface Scattering:}
We have replicated the subsurface scattering process of Ha\v{s}an et al.~\shortcite{Hasan:2010:PRO} using our framework (Figure~\ref{fig:sub}).
The input to our algorithm is a 3D mesh along with subsurface-scattering profiles defined at a set of surface points. We use the same \emph{reducer tree} as in the texture example thereby simplifying the process configuration phase.
The only difference is that we allow each column to have four layers of varying thickness and material. We use a branch and bound optimization algorithm which has been modified to handle continuous parameters by allowing discrete increments. We implement a bound estimate callback function specific to this problem.
Each column is optimized independently using the algorithm. The simulation computes a scattering profile for given a stacking and the error metric compares the simulated and goal profiles using squared error.
%We note that the ability to reuse Reducer Nodes simplifies the configuration of new processes.

\begin{figure}
\centering
\includegraphics[width=0.65\linewidth]{figure/fig_chess.pdf}
\caption{
	A marble chessboard with prescribed subsurface scattering properties.
	The insets show the samples under thin line illumination, and the graph shows the convergence of tuners for 10 out of 100 scattering profiles used in the example. The error is measured by square distance between two profiles, each containing 400 coefficients.}
\label{fig:sub}
\end{figure}

\paragraph{Goal-based Caustics:}
We have configured two different processes for computing goal-based caustics (Figure~\ref{fig:caust2}). While they define exactly the same goal, they have very different \emph{reducer trees} and \emph{tuner networks}.
The first process is based on the work of Papas et al.~\shortcite{Marios:2011}. It computes a set of micro-lenses which produce the desired caustic image. The image is pre-processed into a set of Gaussian distributions. Each distribution is matched with a microlens. The optimization applies simulated annealing to permute the location of these micro-lenses in order to construct a smooth surface. In the \emph{tuner network}, each \emph{tuner} is connected to its four neighbors. During the execution of an individual \emph{tuner}, the optimization algorithm makes a randomized decision about whether or not to swap its micro-lens with one of its neighbors based on smoothness of the surface. The \emph{tuners} are executed many times until a user-specified convergence criterion is met. In our examples, we use $45^2$ microlens and ran all the \emph{tuners} for $2000$ iterations. In the second process, based on the work of Finckh et al.~\shortcite{Finckh:2010}, we use a \emph{B-spline node} to represent a smooth caustic surface. This is in contrast to the potentially discontinuous surface in the method above. The reduced parameters are the height of each spline control point. We implement a simple caustics simulator for height fields. The simulated image is compared to the goal image using mean squared error. We used $60\times 60$ control points and render the simulated image at $240\times 240$ pixel resolution.

\begin{figure}
\centering
\includegraphics[width=0.65\linewidth]{figure/fig_caustic.pdf}
\caption {3D printed lens arrays that each produce a caustic image of Einstein.
Below we show convergence plots for both the microfacet and smooth surface optimizations.
The portrait is available from the United States Library of Congress's Prints and Photographs division,
now in the public domain.
}
\label{fig:caust2}
\end{figure}
%\vspace{-\baselineskip}

\paragraph{Elastic Behavior:}
In the spirit of Bickel et al.~\shortcite{Bickel:2009} we have implemented an algorithm to compute material distribution based on a desired force-displacement response. The input to this algorithm is a mesh, a simulation configuration, and a desired shape. Simulation configuration includes vertex constraints and forces applied to the mesh. For this example, we use a co-rotational finite element method (FEM) simulation with linearly elastic materials to estimate the objects deformation. For the \emph{reducer tree}, we use a voxel partition to divide the object into a low-resolution grid. We assign a single material to each grid cell. The FEM simulator queries the \emph{reducer tree} for material assignments at arbitrary spatial locations. We use the same branch and bound algorithm as in our subsurface-scattering process but with a different bound computation callback function. We use the mean squared distance between the simulated and the desired shapes as the error metric. We have designed a simple experiment to validate our process in which we set the goal of our optimization to be a given deformed state (\autoref{fig:book}).

@@

\paragraph{Combining Caustics and Spatially-varying Albedo:}
The first of our new combined translation processes incorporates both smooth caustics and texture mapping. More specifically, we compute a transparent slab with a texture image that, when illuminated, casts a prescribed caustic image. The input slab is split into two pieces using a \emph{plane node} as shown in Figure~\ref{fig:ReducerTreesAdditional}.
The top piece is tuned to produce an input image. The material in the top piece is then fixed. The bottom piece is then tuned to produce a caustics image.

\paragraph{Combining Deformable Object and Spatially-varying Albedo:}
Our second new process combines spatially-varying albedo and elastic deformation properties. This is a very useful combination since when modeling objects we would like to specify both their appearance and ``feel''. In this process, the input shape is divided into a thin shell and an inner volume. We optimize for the deformation behavior and the texture independently due to the limitations of our current FEM simulator. As the outer shell is very thin, it has negligible influence on overall object deformation.

@@

\chapter{Discussion}
\biglet{T}{hrough} our series of experiments, the \emph{reducer tree} and \emph{tuner network} have allowed us to reuse a large number of software components.
In the extreme case, we arrive at our subsurface scattering algorithm by trivially adapting the same \emph{reducer tree} for texture mapping objects.
The power of component reuse is further elucidated by the presence of \emph{column nodes} in most examples and by our ability to reuse optimization schemes (such as branch and bound) in multiple algorithms.
The \emph{reducer tree} and \emph{tuner network} make these similarities easy to observe and exploit.
The only component whose reusability was not demonstrated in this paper is simulation.
In this work, we have aimed to fabricate objects with a wide range of physical properties and this necessitates the use of a wide range of simulation algorithms. Finally, once a whole process is configured, it is independent of input geometry and goal parameters. For example, we have run the spatially-varying albedo process with different geometries and input textures

The \emph{reducer-tuner model} is ideally suited for multi-material printing capable of producing objects with a wide range of different properties.
In order to showcase these strengths, we have fabricated our examples for an Objet500 Connex -- a phase change inkjet printer that uses photopolymers with a wide range of optical and mechanical properties. Even though only two materials can be used and mixed within a single object, our framework has been proven to be very useful. 
As the number of materials that can be printed simultaneously will grow, we expect the methodology presented here to increase in utility.
For other types of 3D printing technologies, Spec2Fab framework has a reduced use. In the case of 3D printing using a single, rigid material (e.g., fused filament fabrication or Stereolithography) the framework can be used to tune geometry of objects. For plaster-based 3D printers that produce full-color 3D prints, Spec2Fab framework can be employed to compute proper texturing of objects.

>>>>

\chapter{Proposed Experiments}
\label{chap:results}
\begin{figure*}[t]
\includegraphics[width=\linewidth]{figure/TexturedExamples.pdf}
\caption {The reducer-tuner model should enable creating objects of arbitrary shapes with embedded textures.}
\label{fig:texturedExamples}
\end{figure*}
\biglet{I}{n} order to evaluate capabilities of our system, I will implement a number of existing translation processes.
Furthermore, the ease with which different algorithm components can be combined should enable creation of new combinations of translation processes. In this proposal, I will discuss two combinations in detail, while I can potentially make more combinations within the capabilities of the proposed system.
The first combination is an algorithm that can produce objects with desired refractive properties and an associated texture.
The second algorithm applies a desired texture to an object with prescribed deformation behavior.
All of these processes, both from prior work and new ones, should easily fit into our framework. I plan to manufacture the objects using a Stratasys Object500 Connex  multi-material printer.
The following paragraphs provide a detailed description of how the individual algorithms can be designed with my system.
All \emph{reducer trees} and the \emph{tuner networks} for producing these results are presented in \autoref{fig:ReducerTreesAdditional}.

\paragraph{Spatially-varying Albedo:}
I will design a Spec2Fab translator that allows 3D printing of textured models (Figure~\ref{fig:texturedExamples}).
Being able to apply precisely specified spatially-varying albedo values to printed models is a crucial capability.
However, no standard processes have been designed for this task so far.
The input to the texturing algorithm is a shape and its desired albedo texture.
Since the texture is only affected by materials close to the surface, I can use a \emph{stratum node} to divide the input shape into a thin shell and an inner volume.
The outer layer can be divided into columns.
The set of printable colors is expanded by stacking translucent materials using the \verb|LayeredMaterial| Node.
The number of layers is fixed to the number of print materials.
The reduced parameters are the thickness values of each material layer.
For each column, the \emph{tuner}'s optimizer looks up the proper stacking that produces the closest albedo value.
Due to printer resolution, the range of albedo values that can be achieved is quantized.
I therefore can implement an error diffusion algorithm by connecting neighboring \emph{tuners}.
In this simple algorithm, the simulation is a table lookup using measured albedo value corresponding to different base materials.

\paragraph{Heterogeneous Subsurface Scattering:}
I will replicate the subsurface scattering process of Ha\v{s}an et al.~\shortcite{Hasan:2010:PRO} using my framework (Figure~\ref{fig:sub}).
The input to this algorithm is a 3D mesh along with subsurface-scattering profiles defined at a set of surface points. We use the same \emph{reducer tree} as in the texture example thereby simplifying the process configuration phase.
The only difference is that I will allow each column to have four layers of varying thickness and material. 
I will use a branch and bound optimization algorithm which has been modified to handle continuous parameters by allowing discrete increments.
I will implement a bound estimate callback function specific to this problem.
Each column is optimized independently using the algorithm. 
The simulation computes a scattering profile for a given stacking and the error metric compares the simulated and goal profiles using squared error.

\begin{figure}
\centering
\includegraphics[width=0.65\linewidth]{figure/fig_chess.pdf}
\caption{
	A marble chessboard with prescribed subsurface scattering properties produced by Ha\v{s}an et al.~\shortcite{Hasan:2010:PRO}.
	The insets show the samples under thin line illumination, and the graph shows the convergence of tuners for 10 out of 100 scattering profiles used in the example. The error is measured by square distance between two profiles, each containing 400 coefficients.}
\label{fig:sub}
\end{figure}

\paragraph{Goal-based Caustics:}
I will configure two different processes for computing goal-based caustics (Figure~\ref{fig:caust2}). While they define exactly the same goal, they have very different \emph{reducer trees} and \emph{tuner networks}.
The first process is based on the work of Papas et al.~\shortcite{Marios:2011}.
It computes a set of micro-lenses which produce the desired caustic image. The image is pre-processed into a set of Gaussian distributions. Each distribution is matched with a microlens. The optimization applies simulated annealing to permute the location of these micro-lenses in order to construct a smooth surface. In the \emph{tuner network}, each \emph{tuner} is connected to its four neighbors. During the execution of an individual \emph{tuner}, the optimization algorithm makes a randomized decision about whether or not to swap its micro-lens with one of its neighbors based on smoothness of the surface. 
The \emph{tuners} are executed many times until a user-specified convergence criterion is met. 
In the second process, based on the work of Finckh et al.~\shortcite{Finckh:2010}, I will use a \emph{B-spline node} to represent a smooth caustic surface.
This is in contrast to the potentially discontinuous surface in the method above.
The reduced parameters are the height of each spline control point.
I will implement a simple caustics simulator for height fields.
The simulated image is compared to the goal image using mean squared error.

\begin{figure}
\centering
\includegraphics[width=0.65\linewidth]{figure/fig_caustic.pdf}
\caption {3D printed lens arrays that each produce a caustic image of Einstein. The algorithms are proposed by Papas et al.~\shortcite{Marios:2011} and Finckh et al.~\shortcite{Finckh:2010}.
Below we show convergence plots for both the microfacet and smooth surface optimizations.
The portrait is available from the United States Library of Congress's Prints and Photographs division,
now in the public domain.
}
\label{fig:caust2}
\end{figure}
%\vspace{-\baselineskip}

\paragraph{Elastic Behavior:}
In the spirit of Bickel et al.~\shortcite{Bickel:2009}, I will implemented an algorithm to compute material distribution based on a desired force-displacement response.
The input to this algorithm is a mesh, a simulation configuration, and a desired shape.
Simulation configuration includes vertex constraints and forces applied to the mesh.
For this example, I will use a co-rotational finite element method (FEM) simulation with linearly elastic materials to estimate the objects deformation.
For the \emph{reducer tree}, I will use a voxel partition to divide the object into a low-resolution grid.
I will assign a single material to each grid cell.
The FEM simulator queries the \emph{reducer tree} for material assignments at arbitrary spatial locations.
I will use the same branch and bound algorithm as in our subsurface-scattering process but with a different bound computation callback function.
I will use the mean squared distance between the simulated and the desired shapes as the error metric.
I will design a simple experiment to validate this process in which I set the goal of our optimization to be a given deformed state (\autoref{fig:book}).

@@

\paragraph{Combining Caustics and Spatially-varying Albedo:}
The first of my new combined translation processes incorporates both smooth caustics and texture mapping.
More specifically, I will compute a transparent slab with a texture image that, when illuminated, casts a prescribed caustic image.
The input slab is split into two pieces using a \emph{plane node} as shown in Figure~\ref{fig:ReducerTreesAdditional}.
The top piece is tuned to produce an input image. The material in the top piece is then fixed. The bottom piece is then tuned to produce a caustics image.

\paragraph{Combining Deformable Object and Spatially-varying Albedo:}
My second new process combines spatially-varying albedo and elastic deformation properties.
This is a very useful combination since when modeling objects we would like to specify both their appearance and ``feel''.
In this process, the input shape is divided into a thin shell and an inner volume.
I will optimize for the deformation behavior and the texture independently due to the limitations of our current FEM simulator.
As the outer shell is very thin, it has negligible influence on overall object deformation.

@@

\chapter{Discussion}
\biglet{T}{hrough} the above series of experiments, I will confirm whether \emph{reducer tree} and \emph{tuner network} can allow us to reuse a large number of software components.
In the extreme case, the subsurface scattering algorithm can be obtained by trivially adapting the same \emph{reducer tree} for texture mapping objects.
The power of component reuse is further elucidated by the presence of \emph{column nodes} in most examples and by the reuse of optimization schemes (such as branch and bound) in multiple algorithms.
The \emph{reducer tree} and \emph{tuner network} will make these similarities easy to observe and exploit.
The only component whose reusability was not demonstrated in this proposal is simulation.
In this work, I will aim to fabricate objects with a wide range of physical properties and this necessitates the use of a wide range of simulation algorithms. Finally, once a whole process is configured, it is independent of input geometry and goal parameters. For example, I can run the spatially-varying albedo process with different geometries and input textures

The \emph{reducer-tuner model} is ideally suited for multi-material printing capable of producing objects with a wide range of different properties.
In order to showcase these strengths, I will fabricated my examples for an Objet500 Connex -- a phase change inkjet printer that uses photopolymers with a wide range of optical and mechanical properties. Even though only two materials can be used and mixed within a single object, our framework has been proven to be very useful. 
As the number of materials that can be printed simultaneously will grow, we expect the methodology presented here to increase in utility.
For other types of 3D printing technologies, Spec2Fab framework has a reduced use. In the case of 3D printing using a single, rigid material (e.g., fused filament fabrication or Stereolithography) the framework can be used to tune geometry of objects. For plaster-based 3D printers that produce full-color 3D prints, Spec2Fab framework can be employed to compute proper texturing of objects.
